---
title: "Exercise 1B"
format:
  html:
    theme: default
---

## Generation of a histogram of sampled data 

To create the histogram we need to sample the values. Here we are going to sample from a negative binomial distribution. 

The given parameter are 
mu = 10
dispersion =2 
sample size n=100

Since we are sampling random values. It it could be beneficial to use the function set.seed() to get the same "random" values 

```{r}
```


```{r}
set.seed(1) #to get the same results when running the code 
n=100
mu= 10
dispersion = 2

```

## Sampling 
now that we have all needed parameter we can sample

```{r}
x= rnbinom(100, mu=mu,size = 1/dispersion)
x
``` 


## Histograms


### linear scale 
```{r}

hist(x, main = "Histogram of the sampled data (linear)")


``` 
### log scale 
```{r}
hist(log(x+1), xlab = "log(x+1)", main = "Histogram of the sampled data (log)" )
```

##Comparing mean and variance 

**mean and Variance of the sample**
```{r}
mean(x)
var(x)

```

**given parameter**
```{r}
mean = mu
Variance = mu + mu^2 *dispersion

mean
Variance 

```

